% @Author: Taha Bouhsine
\setcounter{mtc}{13}

\chapter*{Conclusion}
\label{chap:conclusion}
\minitoc
\markboth{\MakeUppercase{Conclusion}}{}%
\addcontentsline{toc}{chapter}{Conclusion And Perspective}
\section*{Conclusion}
Ideas are cheap, execution is expensive,
even if you create a beautiful application with
a beautiful User Interface, if you neglect even one aspect of the main functionalities,
and built it with a half effort, you might result in a product that won't live for long,
or if you were to use the wrong technologies for the project, you might as well find yourself
limited and won't be able to create and bring the most out of your Idea.

With this in mind, and from the very start of the project we gave enough time for the design phase,
we aimed to create not a prototype of a project that will be neglected afterward, but a well structured
project, that respects the nowadays requirements, implementing the MEAN stack technologies, and 
multiple layers of security, especially that we have an application that handles payments transactions
and sensible pieces of information, from debit cards to the user's personal information.

And it goes without saying that I learned a lot of different skills during the development of this project,
it helped me to widen my knowledge and use different practices and concepts I acquired throughout my academic
years, and my journey in self-learning. The research on the literature side of this project also helped me 
to link between my coding skills, and the ability to create solutions, as well as the communication skills
I acquired during the rich talks I had with \mentor.

\section*{Perspective}
Unfortunately, due to time, material, and some uncontrollable constraints, I was not able to arrive 
at the result, we had envisioned
for this project. However, this does not mean that the progress of this project is over, with the
previous work we did as the base, there are
still, several aspects and functionalities to include in order for this app to take the shape we
intended for it. This continuous progress will go into the future work category and will include
the following actions:
\begin{itemize}
    \item Creating a native application with Nativescript, reusing the logic we built in Angular.
    \item Move from a monolithic architecture to microservices.
    \item Deploy the platform to a better PaaS such as Google Cloud.
    \item Linking the application with a domain name.
    \item Create an ai model to handle the suggestion to users during the creation of a fundraiser.
    \item Finish the messaging Business Logic.
    \item Finish the posts Business Logic.
    \item Finish the Administration application.
    \item Finish the comment section of a fundraiser.
    \item Improving UX and error handling.
    \item Studying the possibility of integrating Inwi Money or an alternative for Morrocan Users.
\end{itemize}

